Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-06 intro.tex
URL citations

In recent years, there has been a growth of interest in data visualization technologies for human-assisted data analysis using systems such as \cite{Stolte:2008,Qlik,Ahlberg:1996}. While computers can provide high-speed and high-volume data processing, humans have domain knowledge and the ability to process data in parallel, notably by using our visual systems. Most importantly, humans provide the definition of what is valuable in an analysis. Accordingly, human/computer analytic systems are essential to extracting knowledge of value to humans and their societies from the large amounts of data being generated today.

@@

\subsection{Related Work}

Data preparation has been a known analytic bottleneck since at least the description of the Potter's Wheel system~\cite{Ramen:2001}. Since then, several other interactive data preparation systems have been proposed, including Data Wrangler~\cite{Kandel:2001} and Google Refine~\cite{refine}. While effective, these systems all make assumptions about possible date formats (\eg the domain system in~\cite{Ramen:2001}), which we suggest are too restrictive for real world data.

The Minimum Descriptive Length technique was first proposed in Rissanen~\cite{Rissanen:1978}.  We have built on the version described in~\cite{Ramen:2001}.

>>>>

In recent years, there has been a growth of interest in data visualization technologies for human-assisted data analysis using systems such as \cite{Stolte:2008,Ahlberg:1996}. While computers can provide high-speed and high-volume data processing, humans have domain knowledge and the ability to process data in parallel, notably by using our visual systems. Most importantly, humans provide the definition of what is valuable in an analysis. Accordingly, human/computer analytic systems are essential to extracting knowledge of value to humans and their societies from the large amounts of data being generated today.

@@

\subsection{Related Work}
Data preparation has been a known analytic bottleneck since at least the description of the Potter's Wheel system~\cite{Raman:2001}. Since then, several other interactive data preparation systems have been proposed, including Data Wrangler~\cite{Kandel:2011} and Google refine~\cite{Refine}. While effective, these systems all make assumptions about possible date formats (\eg the domain system in~\cite{Raman:2001}), which we suggest are too restrictive for real world data.

The Minimum Descriptive Length technique was first proposed in Rissanen~\cite{Rissanen:1978}.  We have built on the version described in~\cite{Raman:2001}.
